Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex
use paralist and description

We describe our definition of Levels of Detail for Buildings such as:
\begin{itemize}
    \item \textbf{LOD-0:} The most straightforward form, representing buildings as oriented bounding boxes. This level is typically used for large-scale preliminary analyses and quick visual assessments.
    \item \textbf{LOD-1:} Buildings are represented as polygonal extrusions, with added roof structures to improve the visual accuracy and utility in simulations that do not require detailed internal features.
    \item \textbf{LOD-2:} At this level, buildings are detailed using Industry Foundation Classes (IFC) standards, supporting detailed thermal and structural analyses. This includes detailed geometries for each building entity, often using complex surface models like B-REP, swept solids, or CSG techniques.
\end{itemize}

@@

\subsubsection{Terrain Modeling}
The terrain modeling process utilizes elevation data extracted from raster images. The initial step involves creating a uniform mesh based on the size of the raster image. Following this, the elevation at each node is evaluated.
However, this method provides a very refined mesh, even when the terrain is flat. For this reason, we plan to apply a mesh adaptation technique to reduce mesh density where feasible, using the following processing:
\begin{itemize}
    \item Compute an arbitrary number of isolines for elevation,
    \item Build a new terrain mesh conform with the isolines nodes and adapt to terrain elevation gradient.
\end{itemize}
%Subsequently, isolines for elevation are computed, and mesh adaptation techniques are applied to reduce mesh density where feasible. Finally, each tile is glued together to ensure the continuity of the terrain mesh.

@@

Including vegetation (trees) in our geometric model is essential for the simulation of buildings. The shading provided by trees and the cooling provided by wooded areas had a significant impacts on building environment  . We use the OpenStreetMap database to obtain the metadata associated with the vegetation. In addition to the position of the trees, we can also obtain other information, such as the tree's height and species. The current strategy is as follows:

\begin{itemize}
\item Definition of a reference tree library that lists a certain number of tree species at different levels of precision (LOD). These geometric entities are parameterized so that a transformation can be applied.
\item Fetching vegetation metadata via OpenStreetMap. The attributes (height, species) are not always available, so we try to define them as best as we can (by searching around).
\item Creating a tree geometric model using an affine transformation of the reference tree model.
\end{itemize}

@@

Data partitioning is a crucial stage in the deployment of the supercomputer simulator. We need to partition the geometry of the city in such a way as to distribute the simulation computation correctly.
Different partitioning strategies are considered depending on the specific requirements of the simulation use cases :
\begin{itemize}
\item Case 0: simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient
\item Case 1: buildings interact with environmental elements, a more complex partitioning strategy is necessary that considers both the buildings and their immediate non-building surroundings. The build meshes and environment meshes (terrain, vegetation) are integrated conformably; each component can be partitioned separately.
\item Case 2: for full interaction models, the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring all elements are considered to minimize communication overhead.
\item Case 3: Regarding scenarios with extreme partitioning needs, Test Case 3 employs a multi-grid approach, defining coarse and fine meshes to manage computational resources efficiently. This multi-fidelity approach enhances the accuracy and applicability of urban models in simulations and ensures scalability across different computational platforms, making it a cornerstone of urban analysis.
\end{itemize}

@@

We now turn to describing the physical modeling of city energy simulation.

To do this, we built on two main tools: Feel++ and Modelica.

@@

The physical model of city buildings is based on a multizone model.
One zone is allocated per building floor. 
The energy balance for each zone is calculated by taking into account energy exchanges with adjacent zones and the environment.

@@

\paragraph{HVAC heat flow} In the version of the model at the time of writing, the HVAC system is treated as an ideal heat source, which means it adjusts its output to maintain a set temperature within the building.

\paragraph{Heat gain} Heat gain is the addition of energy to the building, derived from two sources: \textbf{internal heat gains} and \textbf{solar heat gains}.

\paragraph{Internal heat gain} The internal heat gain captures the heat produced by occupants inside the building. 
It is modeled as a function of metabolic rate $\mathrm{Met}$ and the number of inhabitants, $d_i$, which varies over time $t$:
\begin{equation}
  \phi_{\mathrm{int}} = \mathrm{Met} \cdot d_i(t)
\end{equation}

\paragraph{Solar heat gain} The total solar heat gain includes contributions from direct, diffuse, and reflected solar radiation, taking into account the building’s surface characteristics and shading coefficient:
\begin{equation}
  \phi_{\mathrm{solar}} = \alpha \cdot S \cdot \left( E_{\mathrm{dir}} + E_{\mathrm{diff}} + E_{\mathrm{ref}} \right) \cdot S_C
\end{equation}
Direct solar radiation is the component of solar radiation adjusted for the angle of incidence of the sunlight:
\begin{equation}
  E_{\mathrm{dir}} = F_{\mathrm{dir}} \cdot \cos(I)
\end{equation}
Here, $F_{\mathrm{dir}}$ is the direct solar radiation, which is a function of the horizontal solar radiation measured by a weather station:
\begin{equation}
  F_{\mathrm{dir}} = \dfrac{F_{\mathrm{dir,Hz}}}{\sin(H_s)}
\end{equation}
The term $\cos(I)$ calculates the cosine of the angle of incidence of sunlight, incorporating the sun's altitude and azimuth angles as well as the building's tilt angle:
\begin{equation}
  \cos(I) = \cos(H_s) \cdot \sin(\beta) \cdot \cos(A_{zs} - A_z) + \sin(H_s) \cdot \cos(\beta)
\end{equation}
Diffuse solar radiation includes contributions from the sky dome and is adjusted for the building's tilt:
\begin{equation}
  E_{\mathrm{diff}} = F_{\mathrm{dif,Hz}} \cdot \left( \dfrac{1 + \cos(\beta)}{2} \right)
\end{equation}
Reflected solar radiation is calculated using the total horizontal radiation and the environment's albedo:
\begin{equation}
  E_{\mathrm{ref}} = \left[ F_{\mathrm{dir,Hz}} + F_{\mathrm{dif,Hz}} \right] \cdot \left( \dfrac{1 + \cos(\beta)}{2} \right) \cdot \text{albedo}
\end{equation}

\paragraph{Conduction losses} Energy loss through walls is computed by summing the losses across all wall segments. It depends on the heat transfer coefficient, the wall area, and the temperature difference between the indoor and outdoor environments. In our current model, we simplify the calculations by not including the effects of thermal bridges, as they depend on specific information about the building's envelope, which we do not have:
\begin{equation}
  \phi_{\mathrm{wall}} = \sum_{j} U_j \cdot S_j \cdot \Delta T
\end{equation}
The convection losses are computed differently depending on the surface of the wall to which they are applied. On the interior surface, we apply a constant:
\begin{equation}
  \phi_{\mathrm{conv,int}} = \alpha_{\mathrm{conv}} \cdot \Delta T
\end{equation}
On the exterior surface, we use a forced convection model:
\begin{equation}
  \phi_{\mathrm{conv,ext}} = \left( 1.8 + 4.8 \cdot v_{\mathrm{air}} \right) \cdot \Delta T
\end{equation}

\paragraph{Radiation losses} Radiation losses describe the heat energy lost due to thermal radiation, impacting both energy efficiency and thermal comfort.
We differentiate between the exterior of the wall that exchanges with the sky and the interior where the walls exchange with each other.
namely, for the exterior radiation exchange:
\begin{equation}
  \phi_{\mathrm{net,sky}} = \varepsilon_i \cdot \sigma \cdot \left( T_i^4 - T_{\mathrm{sky}}^4 \right)
\end{equation}
and for the interior radiation exchange:
\begin{equation}
  J[i] = \varepsilon_i \cdot \sigma \cdot T_i^4 + \left( 1.0 - \varepsilon_i \right) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]
\end{equation}
where the radiative heat exchange $J[i]$ includes two terms:
\begin{inparaenum}[\it (i)]
    \item $\varepsilon_i \cdot \sigma \cdot T_i^4$, which calculates the heat radiated by surface $i$ where $\varepsilon_i$ measures how effectively the surface emits radiation and $T_i^4$ reflects that radiative heat loss increases rapidly with temperature; and
    \item $\left( 1.0 - \varepsilon_i \right) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]$, which accounts for the heat absorbed from other surfaces $j$ within the zone. The factor $\left( 1.0 - \varepsilon_i \right)$ adjusts for the fraction of incoming radiation not emitted by surface $i$.
\end{inparaenum}
The net radiation flow is given by:
\begin{equation}
  \phi_{\mathrm{net,int}}[i] = S \cdot \dfrac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot \left( \sigma \cdot T_i^4 - J[i] \right)
\end{equation}
Net radiation flow $Q_{\mathrm{flow}}[i]$ considers:
\begin{inparaenum}[\it (i)]
    \item $\dfrac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot \left( \sigma \cdot T_i^4 - J[i] \right)$, which calculates the net heat flow due to radiation for surface $i$, considering the difference between the heat emitted by the surface and the heat received from other surfaces. The ratio $\dfrac{\varepsilon_i}{1.0 - \varepsilon_i}$ scales the net flow based on the emissivity of the surface.
\end{inparaenum}

\paragraph{Air change} This term represents the energy loss due to air exchange between the zone and the exterior:
\begin{equation}
  \phi_{\mathrm{air}} = 0.34 \cdot Q_v \cdot \Delta T
\end{equation}

The described thermal models are implemented using the Modelica language, which is an object-oriented, equation-based language well-suited for modeling complex physical systems. 
These models are then transformed into Functional Mock-up Units (FMUs) compliant with the Functional Mock-up Interface (FMI) standard. 
FMUs encapsulate the models and enable them to be shared and integrated across different simulation environments.

@@

\paragraph{Numerical Methods and Challenges}
Both shading masks and view factors are computed using Monte Carlo and ray tracing techniques, which allow for handling complex geometries with various obstructions. Despite being purely geometric quantities, these calculations face significant challenges such as:
\begin{itemize}
    \item Efficient computation of integrals for view factors, especially when considering specular surfaces that require multiple ray bounces.
    \item Managing large-scale mesh computations and data storage, particularly when detailed urban environments are modeled.
\end{itemize}

@@

To run a KUB simulation, several input files need to be generated.
We have several metadata files (in JSON format), mesh data files (in MSH format), and meteorological measurement files (in CSV format).
\Cref{tab:input-data-size-comparison} lists these files with their corresponding sizes for New York City and a duration of one year for the simulation.
In addition, we compared the size of the input data with the size of the zone.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-feelpp-devops.pdf}
    \caption{CI/CD DevOps for Feel++}
    \label{fig:feelpp-devops}
\end{figure}
The CI/CD workflow, see \cref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. 
The workflow leverages various main ingredients of GitHub Actions features.
\begin{enumerate}
    \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
    \item \textbf{Graphical User Interface (GUI) thanks to \texttt{workflow\_dispatch}:} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing.
    \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
\end{enumerate}

@@

To better understand what causes this degradation, we measure the computing times of the different stages of the pipeline and present the execution breakdown in \cref{fig:execution-breakdown}. 
\cref{fig:execution-breakdown} reports the portion of the total execution taken by:
\begin{itemize}
\item Pre-processing (Pre-proc): The time elapsed in initialization before entering the time loop of the simulation
\item Simulation (Simulation): The cumulative time spent calculating the new solution at each time step
\item Post-processing (Post-proc): The cumulative time spent exporting results, i.e., generating files containing the output of the UB model.
\end{itemize}

>>>>

We describe our definition of Levels of Detail for Buildings such as:
\begin{description}
    \item[LOD-0] The most straightforward form, representing buildings as oriented bounding boxes. This level is typically used for large-scale preliminary analyses and quick visual assessments.
    \item[LOD-1] Buildings are represented as polygonal extrusions, with added roof structures to improve the visual accuracy and utility in simulations that do not require detailed internal features.
    \item[LOD-2] At this level, buildings are detailed using Industry Foundation Classes (IFC) standards, supporting detailed thermal and structural analyses. This includes detailed geometries for each building entity, often using complex surface models like B-REP, swept solids, or CSG techniques.
\end{description}

@@

\subsubsection{Terrain Modeling}
The terrain modeling process utilizes elevation data extracted from raster images. The initial step involves creating a uniform mesh based on the size of the raster image. Following this, the elevation at each node is evaluated.
However, this method provides a very refined mesh, even when the terrain is flat. For this reason, we plan to apply a mesh adaptation technique to reduce mesh density where feasible, using the following processing:
\begin{inparaenum}[\it (i)]
    \item Compute an arbitrary number of isolines for elevation,
    \item Build a new terrain mesh conform with the isolines nodes and adapt to terrain elevation gradient.
\end{inparaenum}
%Subsequently, isolines for elevation are computed, and mesh adaptation techniques are applied to reduce mesh density where feasible. Finally, each tile is glued together to ensure the continuity of the terrain mesh.

@@

Including vegetation (trees) in our geometric model is essential for the simulation of buildings. The shading provided by trees and the cooling provided by wooded areas had a significant impacts on building environment  . We use the OpenStreetMap database to obtain the metadata associated with the vegetation. In addition to the position of the trees, we can also obtain other information, such as the tree's height and species. The current strategy is as follows:
\begin{inparaenum}[\it (i)]
\item Definition of a reference tree library that lists a certain number of tree species at different levels of precision (LOD). These geometric entities are parameterized so that a transformation can be applied.
\item Fetching vegetation metadata via OpenStreetMap. The attributes (height, species) are not always available, so we try to define them as best as we can (by searching around).
\item Creating a tree geometric model using an affine transformation of the reference tree model.
\end{inparaenum}

@@

Data partitioning is a crucial stage in the deployment of the supercomputer simulator. We need to partition the geometry of the city in such a way as to distribute the simulation computation correctly.
Different partitioning strategies are considered depending on the specific requirements of the simulation use cases :
\begin{inparadesc}
\item[Case 0] simulate simple scenarios where buildings do not interact with their environment, a basic listing and weighting strategy is sufficient;
\item[Case 1] simulate buildings interact with environmental elements, a more complex partitioning strategy is necessary that considers both the buildings and their immediate non-building surroundings; the build meshes and environment meshes (terrain, vegetation) are integrated conformably; each component can be partitioned separately;
\item[Case 2] simulate full interaction models where the partitioning strategy starts with the buildings and extends to the entire urban mesh, ensuring all elements are considered to minimize communication overhead;
\item[Case 3] simulate scenarios with extreme partitioning and employ a multi-grid approach to  define coarse and fine meshes and manage computational resources efficiently; this multi-fidelity approach enhances the accuracy and applicability of urban models in simulations and ensures scalability across different computational platforms, making it a cornerstone of urban analysis.
\end{inparadesc}

@@

We now turn to describing the physical modeling of city energy simulation.
To do this, we built on two main tools: Feel++ and Modelica.

@@

The physical model of city buildings is currently based on a multizone model.
One zone is allocated per building floor. 
The energy balance for each zone is calculated by taking into account energy exchanges with adjacent zones and the environment.

@@

\begin{description}
  \item[HVAC heat flow] In the version of the model at the time of writing, the HVAC system is treated as an ideal heat source, which means it adjusts its output to maintain a set temperature within the building.
  \item[Heat gain] Heat gain is the addition of energy to the building, derived from two sources: \textbf{internal heat gains} and \textbf{solar heat gains}.
  \item[Internal heat gain] The internal heat gain captures the heat produced by occupants inside the building. 
  It is modeled as a function of metabolic rate $\mathrm{Met}$ and the number of inhabitants, $d_i$, which varies over time $t$:
  \begin{equation}
    \phi_{\mathrm{int}} = \mathrm{Met} \cdot d_i(t)
  \end{equation}

\item[Solar heat gain] The total solar heat gain includes contributions from direct, diffuse, and reflected solar radiation, taking into account the building’s surface characteristics and shading coefficient:
\begin{equation}
  \phi_{\mathrm{solar}} = \alpha \cdot S \cdot \left( E_{\mathrm{dir}} + E_{\mathrm{diff}} + E_{\mathrm{ref}} \right) \cdot S_C
\end{equation}
Direct solar radiation is the component of solar radiation adjusted for the angle of incidence of the sunlight:
\begin{equation}
  E_{\mathrm{dir}} = F_{\mathrm{dir}} \cdot \cos(I)
\end{equation}
Here, $F_{\mathrm{dir}}$ is the direct solar radiation, which is a function of the horizontal solar radiation measured by a weather station:
\begin{equation}
  F_{\mathrm{dir}} = \dfrac{F_{\mathrm{dir,Hz}}}{\sin(H_s)}
\end{equation}
The term $\cos(I)$ calculates the cosine of the angle of incidence of sunlight, incorporating the sun's altitude and azimuth angles as well as the building's tilt angle:
\begin{equation}
  \cos(I) = \cos(H_s) \cdot \sin(\beta) \cdot \cos(A_{zs} - A_z) + \sin(H_s) \cdot \cos(\beta)
\end{equation}
Diffuse solar radiation includes contributions from the sky dome and is adjusted for the building's tilt:
\begin{equation}
  E_{\mathrm{diff}} = F_{\mathrm{dif,Hz}} \cdot \left( \dfrac{1 + \cos(\beta)}{2} \right)
\end{equation}
Reflected solar radiation is calculated using the total horizontal radiation and the environment's albedo:
\begin{equation}
  E_{\mathrm{ref}} = \left[ F_{\mathrm{dir,Hz}} + F_{\mathrm{dif,Hz}} \right] \cdot \left( \dfrac{1 + \cos(\beta)}{2} \right) \cdot \text{albedo}
\end{equation}

\item[Conduction losses] Energy loss through walls is computed by summing the losses across all wall segments. It depends on the heat transfer coefficient, the wall area, and the temperature difference between the indoor and outdoor environments. In our current model, we simplify the calculations by not including the effects of thermal bridges, as they depend on specific information about the building's envelope, which we do not have:
\begin{equation}
  \phi_{\mathrm{wall}} = \sum_{j} U_j \cdot S_j \cdot \Delta T
\end{equation}
The convection losses are computed differently depending on the surface of the wall to which they are applied. On the interior surface, we apply a constant:
\begin{equation}
  \phi_{\mathrm{conv,int}} = \alpha_{\mathrm{conv}} \cdot \Delta T
\end{equation}
On the exterior surface, we use a forced convection model:
\begin{equation}
  \phi_{\mathrm{conv,ext}} = \left( 1.8 + 4.8 \cdot v_{\mathrm{air}} \right) \cdot \Delta T
\end{equation}

\item[Radiation losses] Radiation losses describe the heat energy lost due to thermal radiation, impacting both energy efficiency and thermal comfort.
We differentiate between the exterior of the wall that exchanges with the sky and the interior where the walls exchange with each other.
namely, for the exterior radiation exchange:
\begin{equation}
  \phi_{\mathrm{net,sky}} = \varepsilon_i \cdot \sigma \cdot \left( T_i^4 - T_{\mathrm{sky}}^4 \right)
\end{equation}
and for the interior radiation exchange:
\begin{equation}
  J[i] = \varepsilon_i \cdot \sigma \cdot T_i^4 + \left( 1.0 - \varepsilon_i \right) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]
\end{equation}
where the radiative heat exchange $J[i]$ includes two terms:
\begin{inparaenum}[\it (i)]
    \item $\varepsilon_i \cdot \sigma \cdot T_i^4$, which calculates the heat radiated by surface $i$ where $\varepsilon_i$ measures how effectively the surface emits radiation and $T_i^4$ reflects that radiative heat loss increases rapidly with temperature; and
    \item $\left( 1.0 - \varepsilon_i \right) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]$, which accounts for the heat absorbed from other surfaces $j$ within the zone. The factor $\left( 1.0 - \varepsilon_i \right)$ adjusts for the fraction of incoming radiation not emitted by surface $i$.
\end{inparaenum}
The net radiation flow is given by:
\begin{equation}
  \phi_{\mathrm{net,int}}[i] = S \cdot \dfrac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot \left( \sigma \cdot T_i^4 - J[i] \right)
\end{equation}
Net radiation flow $Q_{\mathrm{flow}}[i]$ considers:
\begin{inparaenum}[\it (i)]
    \item $\dfrac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot \left( \sigma \cdot T_i^4 - J[i] \right)$, which calculates the net heat flow due to radiation for surface $i$, considering the difference between the heat emitted by the surface and the heat received from other surfaces. The ratio $\dfrac{\varepsilon_i}{1.0 - \varepsilon_i}$ scales the net flow based on the emissivity of the surface.
\end{inparaenum}

\item[Air change] This term represents the energy loss due to air exchange between the zone and the exterior:
\begin{equation}
  \phi_{\mathrm{air}} = 0.34 \cdot Q_v \cdot \Delta T
\end{equation}
\end{description}
The described thermal models are implemented using the Modelica language, which is an object-oriented, equation-based language well-suited for modeling complex physical systems. 
These models are then transformed into Functional Mock-up Units (FMUs) compliant with the Functional Mock-up Interface (FMI) standard. 
FMUs encapsulate the models and enable them to be shared and integrated across different simulation environments.

@@

\paragraph{Numerical Methods and Challenges}
Both shading masks and view factors are computed using Monte Carlo and ray tracing techniques, which allow for handling complex geometries with various obstructions. Despite being purely geometric quantities, these calculations face significant challenges such as:
\begin{inparaenum}[\it (i)]
    \item Efficient computation of integrals for view factors, especially when considering specular surfaces that require multiple ray bounces.
    \item Managing large-scale mesh computations and data storage, particularly when detailed urban environments are modeled.
\end{inparaenum}

@@

To run a KUB simulation, several input files need to be generated.
We have several metadata files (in JSON format), mesh data files (in MSH format), and meteorological measurement files (in CSV format).
\Cref{tab:input-data-size-comparison} lists these files with their corresponding sizes for New York City, see~\cref{fig:city-ny-largescale}, and a duration of one year for the simulation.
In addition, we compared the size of the input data with the size of the zone.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-feelpp-devops.pdf}
    \caption{CI/CD DevOps for Feel++}
    \label{fig:feelpp-devops}
\end{figure}
The CI/CD workflow, see \cref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. 
The workflow leverages various main ingredients of GitHub Actions features.
\begin{inparaenum}[\it (1)]
    \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
    \item \textbf{Graphical User Interface (GUI) thanks to \texttt{workflow\_dispatch}:} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing.
    \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
\end{inparaenum}

@@

To better understand what causes this degradation, we measure the computing times of the different stages of the pipeline and present the execution breakdown in \cref{fig:execution-breakdown}. 
\cref{fig:execution-breakdown} reports the portion of the total execution taken by:
\begin{description}
\item[Pre-processing (Pre-proc)] The time elapsed in initialization before entering the time loop of the simulation
\item[Simulation (Simulation)] The cumulative time spent calculating the new solution at each time step
\item[Post-processing (Post-proc)] The cumulative time spent exporting results, i.e., generating files containing the output of the UB model.
\end{description}
